---
title: "lab4"
author: "Team 5"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab4)
```

# Lab4: Creating a Linreg object

For this lab, we created an object generator. The generator will make an object of class *linreg* which, using QR factorization, will create a linear regression model for modeling the relationship between an dependent variable Y and one or more independent variables X. The QR decompostion method.   

To provide numerical stability, we used Households reflectors on the algorithm of QR factorization. More information on QR factorization can be found on [Wikipedia.](https://en.wikipedia.org/wiki/QR_decomposition)  

## Creating a linreg object
As this package is an RC generato, to create the linreg object the following command is needed.  
```
    variable_name <-  linreg$new(data, formula).  
```  
From the command above, variable name, data and formula is provided by the user. Make sure that data is a "data.frame" object and formula is a "formula" object using class(). 

## Fields
The linreg object has the following fields, which can be called with *object_name*$**field**:  

+ **formula** A formula object like x ~ y.  
+ **data** A data frame which contains the formula variables.  
+ **X** The matrix created from formula.  
+ **qr** The QR matrix.  
+ **y** A vector with the independent variable values.  
+ **Q** The matrix Q.  
+ **R** The matrix R.  
+ **coefficients** A vector with the beta coefficients.  
+ **fitted_values** A vector with the predicted values of y.  
+ **residuals** A vector with the residuals (y - fitted_values).  
+ **df** The degrees of freedom.  
+ **Bvar** A vector containing the variance of the coefficients.  
+ **resstdev** A vector with the standard deviation of the residuals.  
+ **t_values** A vector with the t_values of the coefficients.  
+ **p_values** A vector with the p_values of the coefficients.  

## Example
Using the following command  
```{r, eval=FALSE}
linreg_mod <- linreg$new(Petal.Length ~ Species, data=iris)
```  
we will create a linreg object (variable) with a the linear model of Petal Length vs. Species. The object has the name linreg_mod. Using class() we can see the class of linregmod.
```{r, eval=FALSE}
class(linreg_mod)
```  
Then, we can call any of the methods inside linreg_mod with the dollar sign. For example we can see the coefficients, standard error, t_values and p_values with summary().
```{r, eval=FALSE}
linreg_mod$summary()
``` 
See all the methods available in the documentation, using ?`linreg-class`
```{r, eval=FALSE}
?`linreg-class`
``` 